### 2020-10-25 latex/symbols.tex
Better motivaated why VNHCss are important and why we study the VLP
Made Theorem numbers as chapter.num
Fully completed / edited VNHCs, we are now at v1.
Made all edits suggested by Manfredi on Oct 19

% Define a table for the symbols using the booktabs convention
\noindent
\begin{table}[h!]
\resizebox{\textwidth}{!}{%
\centering
\begin{tabular}{ll}
   \toprule
   Symbol & Definition \\
   \midrule
   \(\n\) & The index set \(\{1,\ldots,n\}\) of natural numbers up to \(n\). \\
   \(\R^n\) & Real numbers in \(n\) dimensions. \\
   \(\Rt{T}\) & Real numbers modulo \(T > 0\), with \(\Rt{\infty} = \R\). \\
   \(\mathbb{S}^1\) & The unit circle, equivalent to \(\Rt{2\pi}\). \\
   \(\mathcal{Q}\) & The configuration manifold of a system. \\
   \(\R^{n \times m}\) & The space of real-valued matrices with \(n\) rows and \(m\) columns. \\
   \(\Id{n}\) & The \(n \times n\) identity matrix. \\
   \(\Zmat{n \times m}\) & The \(n \times m\) matrix of all zeros. \\
   \(M_i\) & If \(M\) is a vector, the \(i\)th element of \(M\). \\
         & If \(M\) is a matrix, the \(i\)th column of \(M\). \\
   \(M_{i,j}\) & The value of row \(i\), column \(j\) for the matrix \(M\). \\
   \(\dot{x}\) & Derivative of \(x\) with respect to time \(t\). \\
   \(\nabla_v F\) & If \(F\) is \(\R\)-valued, the gradient of \(F\) with respect to \(v\). \\
            & If \(F : \R^m \rightarrow \R^{n\times n}\), the block matrix gradient \((\pdiff{F}{v_1},\ldots,\pdiff{F}{v_m}) \in \R^{nm \times n}\). \\
   \(dF_v\) & Total differential (Jacobian) of \(F\), equivalent to \((\nabla_v F)\tpose\). \\
   \(\Hess F\) & If \(F : \R^n \rightarrow \R\), the \(n \times n\) Hessian matrix of double derivatives of \(F\). \\
               & If \(F : \R^n \rightarrow \R^k\), the block matrix \((\Hess F_1, \ldots, \Hess F_k) \in \R^{n \times nk}\). \\
   \(\partial_v \partial_w F\) & Derivative matrix of \(F : \R^n \times \R^m \rightarrow \R\), with \((i,j)\) element \(\ppdiff{F}{v_i}{w_j}\). \\
   \(\delta_{i,j}\) & The Kronecker delta: 1 if \(i = j\) and 0 otherwise. \\
   \(\otimes\) & The matrix kronecker product (see Appendix \ref{appendix:matrix-kron-prod}). \\
   \bottomrule
\end{tabular}

>>>>

% Define a table for the symbols using the booktabs convention
\noindent
\begin{table}[h!]
\resizebox{\textwidth}{!}{%
\centering
\begin{tabular}{ll}
   \toprule
   Symbol & Definition \\
   \midrule
   \(\n\) & The index set \(\{1,\ldots,n\}\) of natural numbers up to \(n\). \\
   \(\R^n\) & Real numbers in \(n\) dimensions. \\
   \(\Rt{T}\) & Real numbers modulo \(T > 0\), with \(\Rt{\infty} = \R\). \\
   \(\mathbb{S}^1\) & The unit circle, equivalent to \(\Rt{2\pi}\). \\
   \(\mathcal{Q}\) & The configuration manifold of a system. \\
   \(C^r(X;Y)\) & The space of \(r\)-times continuously differentiable functions from \(X\) to \(Y\). \\
         & If \(r = \infty\), the space of smooth functions from \(X\) to \(Y\). \\
   \(\R^{n \times m}\) & The space of real-valued matrices with \(n\) rows and \(m\) columns. \\
   \(\Id{n}\) & The \(n \times n\) identity matrix. \\
   \(\Zmat{n \times m}\) & The \(n \times m\) matrix of all zeros. \\
   \(M_i\) & If \(M\) is a vector, the \(i\)th element of \(M\). \\
         & If \(M\) is a matrix, the \(i\)th column of \(M\). \\
   \(M_{i,j}\) & The value of row \(i\), column \(j\) for the matrix \(M\). \\
   \(\dot{x}\) & Derivative of \(x\) with respect to time \(t\). \\
   \(\nabla_v F\) & If \(F\) is \(\R\)-valued, the gradient of \(F\) with respect to \(v\). \\
            & If \(F\) is \(\R^{n\times n}\)-valued and \(v \in \R^m\), the block gradient \(\left[\nabla_{v_1}F\tpose \ldots \nabla_{v_m}F\tpose\right]\tpose \in \R^{nm \times n}\). \\
   \(dF_v\) & Total differential (Jacobian) of \(F\), equivalent to \((\nabla_v F)\tpose\). \\
   \(\Hess F\) & If \(F : \R^n \rightarrow \R\), the \(n \times n\) Hessian matrix of double derivatives of \(F\). \\
               & If \(F : \R^n \rightarrow \R^k\), the block matrix \((\Hess F_1, \ldots, \Hess F_k) \in \R^{n \times nk}\). \\
   \(\partial_v \partial_w F\) & Derivative matrix of \(F : \R^n \times \R^m \rightarrow \R\), with \((i,j)\) element \(\ppdiff{F}{v_i}{w_j}\). \\
   \(\delta_{i,j}\) & The Kronecker delta: 1 if \(i = j\) and 0 otherwise. \\
   \(\otimes\) & The matrix kronecker product. \\ 
   \(\norm{\cdot}\) & The euclidean norm on \(\R^n\). \\
   \bottomrule
\end{tabular}
